### 2022-04-06 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@c838ae68a102dec3d41800888666f71828b1239a 🚀

Spillover risk is not unidimensional. From the standpoint of an animal
community, i.e.~a pool of possible hosts, there are a multiplicity of
ecological factors that come into play (Plowright et al.~2017). The
global richness of hosts is one such component commonly
mentioned/analysed (Anthony et al.~2017), but there is an argument to be
made that species who are not competent hosts of a specific virus genus
may not factor into this (Plowright et al.~2015), or that species who
are assumed to share viruses at different rates should be weighted
accordingly (Albery et al.~2020). In mammals, key functional traits (for
which phylogeny is a reasonable proxy) are determinants of the spillover
potential (Olival et al.~2017); these include, notably, TK. Finally,
especially when the pool of potential hosts spans the entire globe,
there may be local host pools that are highly unique; not having been
observed in other locations, these can act on the overall risk either by
providing novel contact opportunities, reflecting unique
host-environment combinations (Engering et al.~2013), or facilitating
rapid changes in specialism (Agosta et al.~2010). In the specific case
of generalist pathogens (as betacoronavirus clearly are), there is
conceptual and empirical support to the idea that these community- level
mechanisms are even more important in driving the overall risk (Power
and Mitchell 2004).

@@

>>>>

Spillover risk is not unidimensional. From the standpoint of an animal
community, i.e.~a pool of possible hosts, there are a multiplicity of
ecological factors that come into play (Plowright et al. 2017). The
global richness of hosts is one such component commonly
mentioned/analysed (Anthony et al.~2017), but there is an argument to be
made that species who are not competent hosts of a specific virus genus
may not factor into this (Plowright et al. 2015), or that species who
are assumed to share viruses at different rates should be weighted
accordingly (Albery et al.~2020). In mammals, key functional traits (for
which phylogeny is a reasonable proxy) are determinants of the spillover
potential (Olival et al.~2017); these include, notably, TK. Finally,
especially when the pool of potential hosts spans the entire globe,
there may be local host pools that are highly unique; not having been
observed in other locations, these can act on the overall risk either by
providing novel contact opportunities, reflecting unique
host-environment combinations (Engering et al. 2013), or facilitating
rapid changes in specialism (Agosta et al. 2010). In the specific case
of generalist pathogens (as betacoronavirus clearly are), there is
conceptual and empirical support to the idea that these community- level
mechanisms are even more important in driving the overall risk (Power
and Mitchell 2004).

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Agosta2010HowSpe}{}%
Agosta, S. J. et al. 2010. How specialists can be generalists: Resolving
the {``parasite paradox''} and implications for emerging infectious
disease. - Zoologia (Curitiba) 27: 151--162.

\leavevmode\hypertarget{ref-Engering2013PatHos}{}%
Engering, A. et al. 2013. Pathogen--host--environment interplay and
disease emergence. - Emerging Microbes \& Infections 2: e5.

\leavevmode\hypertarget{ref-Plowright2015EcoDyn}{}%
Plowright, R. K. et al. 2015. Ecological dynamics of emerging bat virus
spillover. - Proceedings of the Royal Society B: Biological Sciences
282: 20142124.

\leavevmode\hypertarget{ref-Plowright2017PatZoo}{}%
Plowright, R. K. et al. 2017. Pathways to zoonotic spillover. - Nature
Reviews Microbiology 15: 502--510.

\end{CSLReferences}
